---
title: "formative.rmd"
author: "R. Glazer"
date: "10/6/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r upload}
setwd("~/Desktop")
D1 <- read.csv("HMXPC13_DI_v2_5-14-14.csv")
View(D1)

```

###5. What does the DI suffix that is appeneded to two of the variable names mean?

Not sure.  There are numerous places where there is a DI suffix - for user ID, for final_cc_cname which corresponds to the location, for start and end dates and LoE, but not sure the correlation.

###6. How many people enrolled in HarvardX/CS50x recieved certification in 2012?

1287
```{r Harvard}
library(dplyr)
D1$CS50x <- with(D1, ifelse(D1$course_id == "HarvardX/CS50x/2012", 1, 0))
CS50 <- filter(D1, D1$CS50x != 0)
table(CS50$certified)
```

###7. How many people registered for HarvardX/CS50x from Columbia on October 15, 2012?

10
```{r Colombia}
CS50$Colombia <- with(CS50, ifelse(CS50$final_cc_cname_DI == "Colombia", 1, 0))
CS50_Colombia <- filter(CS50, CS50$Colombia != 0)
table(CS50_Colombia$start_time_DI)
```

###8. Create a new data frame (D2`) that includes student ID and registration date for all students from a country of your choice
```{r Canada}
D2 <- filter(D1, D1$final_cc_cname_DI == "Canada")
keeps <- c("userid_DI", "start_time_DI")
D2 <- D2[keeps]
```

###9. Create a new data frame (`D3`) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a `1` if the student registered on that date or an `NA` if they did not 
```{r}
#D3 <- 
```
I'm stumped

...and that concludes my 90 minutes (approximately)
